Whole-chromosome pairwise alignment using a hierarchical wavefront algorithm

### 2021-06-01 manuscript/main.tex
started the Result section

    Text Text Text Text Text Text Text Text Text Text Text Text Text
    Text Text Text Text Text Text Text Text.

>>>>

    We evaluated the performance of \wfmash\ 0.xx against Minimap2-v2.20-r1061 {29750242} and Winnomap 2.03 {XXX}, in
    terms of runtime and memory usage. The comparison was performed on both simulated and real datasets. Simulated
    data allowed evaluating the alignment quality by calculating precision and recall in variant identification.
    The evaluations were performed on a workstation running Ubuntu 20.04 equipped with 64 GB of RAM and an Intel i9-9900K
    CPU with 8 cores (16 threads). All commands are provided in the Supplementary Material.

    \subsection{Simulated data}
    We simulated long sequences from the \textit{Saccharomyces cerevisiae} chromosome IV (S288C strain) and
    the telomere-to-telomere (T2T) assemblies of the human chromosomes 8, at different levels of divergence and length
    (Table 1 and Table 2). Chromosomes were split into shorter sequences using the splitfa tool~\citep{splitfa}. In each
    run, all sequences have the same length. Single nucleotide variants (SNVs), small indels, and structural
    variants (SVs) were introduced using the Mutation-Simulator script~\citep{32780803}.
    %, while structural variants (SVs) were applied using the SURVIVOR benchmarking tool~\citep{28117401}.

    To evaluate the correctness of the alignments, we used the pairwise alignment of the input sequences to build
    a pangenome graph in each run, and called the variants on the graphs. The graphs were built using~\citep{seqwish}.
    seqwish implements a lossless conversion from pairwise alignments between sequences to a pangenome graph encoding the
    sequences and their alignments. We called SNVs, small indels, and SVs using vg deconstruct~\citep{30125266},
    evaluating the false-negative and false-positive rates (FNR, FPR) using vcfeval~\citep{vcfeval}.

    \begin{table}[!t]
        \processtable{
            \small
            Performance of pairwise alignment of long sequences from the \textit{Saccharomyces cerevisiae}
            chromosome IV.
            \label{Tab:01}} {
            \begin{tabular}{@{}llllllll@{}}
                \toprule Aligner & Divergence & Length & Runtime (mm:ss) & Memory (GB) & Precision & Sensitivity & F-measure \\
                \midrule
                row1             & row1       & row1   & row1            & row1        & row1      & row1        & row1      \\
                row2             & row2       & row2   & row2            & row1        & row1      & row1        & row1      \\
                row3             & row3       & row3   & row3            & row1        & row1      & row1        & row1      \\
                row4             & row4       & row4   & row4            & row1        & row1      & row1        & row1      \\
                \botrule
            \end{tabular}
        }

    \end{table}

    \subsection{Real data}
    % HPRC data time/memory
    % Histogram of the contig length distribution (supplementary?)
